Measuring Political Freedom Around the World

### 2020-11-16 slides.Rmd
fixed homoscedasticity

kable(t1, align = "c") %>%
  kable_styling(position = "float_left", full_width = F, html_font = "Cambria") %>% 
  row_spec(3, color = "white", background = "#3C989E")

kable(t2, align = "c") %>%
  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria")
```

@@

kable(t1, align = "c") %>%
  kable_styling(position = "float_left", full_width = F, html_font = "Cambria") %>% 
  row_spec(3, color = "white", background = "#3C989E")

kable(t2, align = "c") %>%
  kable_styling(full_width = FALSE, position = "left", html_font = "Cambria") %>% 
  row_spec(3, color = "white", background = "#3C989E")
```

@@

--
### Finite Mean and Standard Deviation
### Independence
### Linearity
### Normality
### Homoskidasticity

>>>>

kable(t1, align = "c") %>%
  kable_styling(position = "float_left", full_width = F) %>% 
  row_spec(3, color = "white", background = "#3C989E")

kable(t2, align = "c") %>%
  kable_styling(full_width = FALSE, position = "left")
```

@@

kable(t1, align = "c") %>%
  kable_styling(position = "float_left", full_width = F) %>% 
  row_spec(3, color = "white", background = "#3C989E")

kable(t2, align = "c") %>%
  kable_styling(full_width = FALSE, position = "left") %>% 
  row_spec(3, color = "white", background = "#3C989E")
```

@@

--
### Finite Mean and Standard Deviation
### Independence
### Linearity
### Normality
### Homoscedasticity
